---
output: md_document
---
```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
setwd("D:/Users/Dinnage/Projects/MEPHEO-blog/")
source("D:/Users/Dinnage/Projects/MEPHEO-blog/Little-Planets/plot.phylo.add.R")
```

Just for fun, we can even use these little planets as a cool backdrop for a circular phylogeny.

```{r littleplanet, warning=FALSE, fig.height=8, fig.width=8, cache=TRUE}
library(jpeg)
library(treebase)
library(ape)
library(wesanderson)
## load little planet image
backimg <- readJPEG("D:/Users/Dinnage/Projects/MEPHEO-blog/Little-Planets/HerdsmanLake_edit_small_centred4.jpg")
## grab a tree for waterfowl
tree <- search_treebase("3269","id.tree","tree",TRUE)
par(bg="gray")
## setup the tree plot
tt<-plot(tree[[1]], type="fan", plot=FALSE, no.margin=TRUE)
## plot the background image on the blank plot
rasterImage(backimg, tt$x.lim[1], tt$y.lim[1], tt$x.lim[2], tt$y.lim[2])
## draw tree with thick green branches
plot.phylo.add(tree[[1]], type="fan",cex=0.75, edge.color=wes.palette(4, "Rushmore")[3],edge.width=6, label.offset=0.1,
               node.depth=2)
## redraw tree with thinner white branches, to give an outline effect
plot.phylo.add(tree[[1]], type="fan",cex=0.75, edge.color="white",edge.width=4, label.offset=0.1,
               node.depth=2)

```

This could probably use some tweaking in a graphics program. As it is, it looks a bit busy. But it was fun to try this in R. By the way, in case you are wondering, the function `plot.phylo.add()` is just the `plot.phylo()` function from the package `ape`, slightly modified so it will plot over something that has already been plotted. I simple commented out this line:

```{r mod, eval=FALSE}
plot.default(0, type = "n", xlim = x.lim, ylim = y.lim, xlab = "", 
             ylab = "", axes = FALSE, asp = asp, ...)
```

That is the line where the function sets up the plot before it draws the tree. Since the plot had already been setup, this line isn't needed, and if it is still there, it results in the plot being redrawn and losing the background image.

What would make this plot even cooler would be to put little silouette [icons](http://descienceblog.tumblr.com/post/85222972145/icons) of the species at the tips. I will work on that.